---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# statsAndBooze

<!-- badges: start -->
<!-- badges: end -->

The goal of statsAndBooze is to find the optimal date for a happy hour, i.e. the closest date when all the participants are available.

## Installation

You can install the development version of statsAndBooze from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("Anastasia-psy/statsAndBooze")
```

## Usage and Examples

To load the package:

```{r}
library(statsAndBooze)
```

The input must be a list of names with the available dates for each participant and must be transformed from string to data format. Use the function `parse_dates()` for this task.

In the list, you must specify the dates in `YYYY-MM-DD` format like in the example below:
```{r}
dates<- list(
  andrea = "2023-03-29", # exactly with this format
  federico = "2023-03-30" # exactly with this format
)

parse_dates(dates)
```

You can also specify a time interval when a participant is available. This must be
done in the following format: `YYYY-MM-DD / YYYY-MM-DD` (see example).


```{r}
dates <- list(
  andrea = c("2023-04-01", "2023-04-03 / 2023-04-05"),
  federico = c("2023-04-02", "2023-04-03"),
  chiara = "2023-04-02 / 2023-04-03"
)

parse_dates(dates)
```

You can also specify the dates using the workdays names in your local language in the abbreviated form. To see the available values for days of week, run the function `lubridate::wday(x, label = TRUE)`.The names of the weekdays refer to the subsequent 7 days with respect to the current day (included) when the function is run. For each person the dates must be specified or in date form or as days of the week, but not in a mixed form. See the following example:
 
```{r lubridate}
lubridate::wday("2023-04-28", label = TRUE)

dates <- list(
  andrea = c("sab", "gio", "dom"),
  federico = c("2023-04-27", "2023-04-30"),
  chiara = "2023-04-28 / 2023-04-30"
)

parse_dates(dates)
```

Finally, to define the date for a happy hour, you need the function `decide_happy_hour()`, which takes the output of the function `parse_dates` as input. In case there are several dates when all the participants are available, the function returns the nearest suitable date. See the example below.

```{r}
dates <- list(
  andrea = c("sab", "gio", "dom"),
  federico = c("2023-04-27", "2023-04-30"),
  chiara = "2023-04-28 / 2023-04-30"
)

parsed_dates <- parse_dates(dates)

decide_happy_hour(parsed_dates)
```

The function returns `Date of length 0` if there is no date when all the participants are available.
